---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

### `unique()`

We previously learned that this is an `"integer"` (*a subtle hint for detecting integers is that they print to the screen without quotes*).

The `unique()` function returns the distinct values in an object (i.e. *duplicate elements/rows removed*). To see how `unique()` works we'll use a vector of duplicate characters (`dups`)

```{r prepare-dups, echo=FALSE}
dups <- c("a", "a", "a", "b", "b", "b", "c", "c", "c")
```

```{r dups, exercise.setup="prepare-dups", exercise=TRUE, exercise.lines=3}
# print dups to the screen
dups
```

Use the `unique()` function below to get the distinct values in `dups`.

```{r unique, exercise.setup="prepare-dups", exercise=TRUE, exercise.lines=3}
# get the unique values in dups 
unique()
```


```{r unique-solution}
unique(dups)
```

```{r unique-check}
gradethis::grade_this_code()
```

`unique()` removes the duplicate values for `"a"`, `"b"`, and `"c"`. 

### `length()`

Use the `length()` function on letters below: 

```{r length, exercise=TRUE, exercise.lines=3}
length()
```

```{r length-solution}
length(letters)
```

```{r length-check}
gradethis::grade_this_code()
```

`length()` returns a value that tells us how many elements are in `letters`. In the code chunk below, use `typeof()` to investigate the return value from `length()`: 

```{r typeof-length, exercise=TRUE, exercise.lines=3}
typeof(x = length(x = ))
```

```{r typeof-length-solution}
typeof(x = length(x = letters))
```

```{r typeof-length-check}
gradethis::grade_this_code()
```

### `str()`

`str()` stands for structure, and returns multiple characteristics on the element we provide. Use `str()` on `letters` below:

```{r structure, exercise=TRUE, exercise.lines=3}
str()
```

```{r structure-solution}
str(letters)
```

```{r structure-check}
gradethis::grade_this_code()
```

+ `chr` is the `class` or `type` (`"character"` in this case) 

+ `[1:26]` is the `length()` or indexed length of the object 

+ `"a" "b" "c" "d" "e" "f" "g" ...` an abbreviate transposed printing of the object (the amount that's printed depends on `options(width = )`). Experiment with different widths in the code block below:

```{r options, exercise=TRUE, exercise.lines=4}
# set multiple values to width
options(width = )
# check the structure of letters and notice the print width
str(letters)
```

```{r reset-options, echo=FALSE}
options(width = 70)
```
